Unified Linear Speedup Analyses of Communication-Efficient Stochastic FedAvg and Nesterov FedAvg

### 2021-07-18 source/main.tex
change table 1
Update on Overleaf.

\newpage
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{fig/bio_zhaonan.jpg}}]{Zhaonan Qu}
Zhaonan Qu is a PhD student in the Department of Economics at Stanford University. His research interests include optimization, machine learning, and causal inference. He received a B.S. in mathematics from Princeton University and an M.A. in mathematics from NYU's Courant Institute.
\end{IEEEbiography}

% if you will not have a photo at all:
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{fig/bio_kaixiang.png}}]{Kaixiang Lin}
Dr. Kaixiang Lin received his Ph.D. degree in Computer Science at Michigan State University in 2020. He regularly serves as a program committee member or reviewer for top-tier machine learning/data ming conferences/journals, including Neurips, ICML, ICLR, TKDE, etc.
% Before joining MSU, he received the B.S. degree from the University of Science and Technology of China, Hefei, China, in 2014. 
\end{IEEEbiography}

>>>>

\newpage
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{fig/bio_zhaonan.jpg}}]{Zhaonan Qu}
Zhaonan Qu is a PhD student in the Department of Economics at Stanford University with a PhD Minor in Operations Research. His research interests include optimization, machine learning, and causal inference. He is supported by a Stanford Interdisciplinary Graduate Fellowship. He received a B.S. in mathematics from Princeton University and an M.A. in mathematics from NYU's Courant Institute.
\end{IEEEbiography}

% if you will not have a photo at all:
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{fig/bio_kaixiang.png}}]{Kaixiang Lin}
Dr. Kaixiang Lin received his Ph.D. degree in Computer Science at 
Michigan State University in 2020. His research interests include 
reinforcement learning, data mining, and machine learning. 
He regularly serves as a program committee member or reviewer for top-tier machine learning/data ming conferences/journals, including Neurips, ICML, ICLR, TKDE, etc.
% Before joining MSU, he received the B.S. degree from the University of Science and Technology of China, Hefei, China, in 2014. 
\end{IEEEbiography}
